Windowed Developer Topic Analysis

### 2009-03-16 lda-paper.tex
changed the lda paper more, added much more stuff very draft like including new figures ripped from presentation

\documentclass[times, 10pt,twocolumn]{article} 
\usepackage{times}

@@

\author{Abram Hindle and Michael Godfrey and Ric Holt \\
\{ahindle,migod,holt\}@cs.uwaterloo.ca\\
Software Architecture Group (SWAG)\\
University of Waterloo\\
}
\title{Windowed Developer Topic Analysis}

@@

@@

\section{Methodology}

@@

@@

@@

\section{Results}
%   1. Interesting smears 
%   2.   postgresql
\subsection{Postgresql}
%   3.   mysql
\subsection{Mysql}
%   4.   firebird
\subsection{Firebird}
%   5.   what's that other db?
\subsection{ what's that other db?}
%7.   Validation [0/1]

\subsection{Compare to topics over entire development}

@@

%   1.   validation
%   2.   LDA is questionable
%   3.   blackbox problem
%   4.   not in the token
%   5.   multiple X token
%9.    Future Work
\section{ Future Work}
%10.   Conclusions
\section{Conclusions}
%11.   Start file file:/home/abez/projects/lda-paper/lda-paper.tex

\bibliographystyle{alpha}
\bibliography{lda-paper}

>>>>

\documentclass[times, 10pt,twocolumn]{article} 
\usepackage{latex8}

@@

\author{Abram Hindle and Michael Godfrey and Ric Holt \\
\{ahindle,migod,holt\}@cs.uwaterloo.ca\\
Software Architecture Group (SWAG)\\
University of Waterloo\\
}

\title{Windowed Developer Topic Analysis}

@@

\newcommand{\affaddr}[1]{#1}
\newcommand{\aemail}[1]{#1}
%\numberofauthors{5}
\author{
%\alignauthor
Abram Hindle\\
%\affaddr{David Cheriton School of Computer Science}\\
\affaddr{University of Waterloo}\\
\affaddr{Waterloo, Ontario}\\
\affaddr{Canada}\\
\aemail{ahindle@cs.uwaterloo.ca}
%\alignauthor
\and
Michael W. Godfrey\\
%\affaddr{David Cheriton School of Computer Science}\\
\affaddr{University of Waterloo}\\
\affaddr{Waterloo, Ontario}\\
\affaddr{Canada}\\
\aemail{migod@cs.uwaterloo.ca}
%\alignauthor
\and
Richard C. Holt\\
%\affaddr{David Cheriton School of Computer Science}\\
\affaddr{University of Waterloo}\\
\affaddr{Waterloo, Ontario}\\
\affaddr{Canada}\\
\aemail{holt@cs.uwaterloo.ca}
%\alignauthor
%\and
%Gregorio Robles\\
%\affaddr{GSyc}\\
%\affaddr{Universidad Rey Juan Carlos}\\
%\affaddr{Madrid}\\
%\affaddr{Spain}\\
%\aemail{grex@gsyc.escet.urjc.es}
}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.9\textwidth]{lda}
  \caption{Example of topics extracted from MySQL 3.23. This is the kind of plot we eventually want to produce: named topics and topic trends}
  \label{fig:lda}
\end{figure*}

\section{Methodology}
\begin{figure*}
  \centering
  \includegraphics[width=0.9\textwidth]{commit-to-topics} 
  \caption{How commits are analyzed and aggregated into Topics and Trends}
  \label{fig:commits}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{transitiveclosure}
  \caption{Clusting topics by the transitive closure of topic similarity. Nodes are topics and arcs imply similarity}
\label{fig:closure}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=1.0\textwidth]{fixed-time-smear-plot-scaled}
  \caption{Compact Trend Plot Topics per Month for MaxDB 7.500}
  \label{fig:topicsmear}
\end{figure*}

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fixed-time-smear-plot-cropped}
  \caption{Zoomed in Slice Compact Trend Plot of Topics per Month for MaxDB 7.500}
  \label{fig:zoomedsmear}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{class-smear-plot-crop-scaled}
  \caption{Trend Time Line: Trends plotted over time of MaxDB 7.500}         
  \label{fig:trendtimeline}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{histogram-cropped-scaled}
  \caption{Top part of trend histogram, ordered by topic occurance for MaxDB 7.500}       
  \label{fig:histogram}
\end{figure}

@@

\section{Results}
%   1. Interesting smears 
%   2.   postgresql
\subsection{Postgresql}
%   3.   mysql
\subsection{Mysql}
%   4.   firebird

XXX need results!

\subsection{Firebird}
%   5.   what's that other db?

XXX needs results

\subsection{MaxDB 7.500}

\subsection{Compare to topics over entire development}
\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{maxdb7500-everything-by-month}
  \caption{MaxDB 7.500 Topics Analyzed with Static Topic Analysis, 20
    topics over the entire development history of MaxDB 7.500. Each
    box indicates the number of documents matching that topic in that
    month.}
  \label{fig:statictopics}
\end{figure}

@@

%   1.   validation
%   2.   LDA is questionable
%   3.   blackbox problem
%   4.   not in the token
%   5.   multiple X token
%9.    Future Work

%10.   Conclusions

\section{Conclusions}
%11.   Start file file:/home/abez/projects/lda-paper/lda-paper.tex

\subsection{ Future Work}

One avenue of future work we think is quite important is automatic
cluster labelling. Given a word distribution we should be able to
figure out a word or term which best describes that distribution
automatically.
Another avenue we wish to investigate the is value of applying
static community generated software taxonomies to the naming or
grouping of clusters

\bibliographystyle{latex8}
\bibliography{lda-paper}

%\bibliographystyle{abbrv}

\section{Appendix}

\begin{itemize}
\item We are missing a comparison of our technique to the classical technique
\end{itemize}
